\documentclass[letterpaper,12pt,nocolor,final]{moderncv} 
\moderncvtheme[red]{casual} % classic or casual

\usepackage[utf8]{inputenc}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\recomputelengths

\usepackage{newtxtext, stix}
\usepackage{amsmath, amsfonts}
\usepackage{microtype}

\usepackage[
  backend=biber,
  style=verbose,
  sorting=none,
  url=false,
  doi=false,
  isbn=false,
  maxnames=99,
]{biblatex}
\addbibresource{mywork.bib}

\firstname{William C.}
\familyname{Dawn}
\title{Curriculum Vitae}
\address{1422 Pitching Wedge Drive, Apt. 205}{27603 Raleigh, NC}
\mobile{(540) 645-2576}
\email{wcdawn@ncsu.edu}
\social[github]{wcdawn}

\begin{document}
\maketitle

\nocite{*}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------

\section{Education}  

  \cventry{May 2022}{Ph.D. Student, Nuclear Engineering}
    {North Carolina State University}{Raleigh, NC}{}{
    Research related to fast reactor physics simulations and design calculations.\\
    Interested in scalable Finite Element Methods and Exascale computing.}
  \vspace{\topsep}

  \cventry{May 2019}{Master of Science, Nuclear Engineering}
    {North Carolina State University}{Raleigh, NC}{}{
    Nuclear Engineering University Program (NEUP) Fellow \\
    Developed simulation suite to model Sodium-cooled Fast Reactors (SFRs).
    \vspace{-1\topsep}
    \printbibliography[keyword={mastersthesis},heading=none]}
  \vspace{\topsep}

  \cventry{May 2017}{Bachelor of Science, Nuclear Engineering}
    {North Carolina State University}{Raleigh, NC}{}{
    Graduated as Valedictorian and \textit{Summa Cum Laude}.
    Led senior design team. Responsible for project management and interfacing with corporate sponsor. \\
    Senior Design Project: ``A Thermal Test Location in a Sodium Cooled Fast Reactor''}

%-------------------------------------------------------------------------------
% PUBLICATION SECTION
%-------------------------------------------------------------------------------

\section{Publications}
  \printbibliography[keyword={publications},heading=none]

\section{Technical Reports}
  \printbibliography[keyword={techreport},heading=none]


%-------------------------------------------------------------------------------
% PATENTS SECTION
%-------------------------------------------------------------------------------

\section{Patents}
  \printbibliography[keyword={patents},heading=none]

%-------------------------------------------------------------------------------
% CONFERENCE PRESENTATIONS SECTION
%-------------------------------------------------------------------------------

\section{Conference Presentations}
  \printbibliography[keyword={conferencepresentations},heading=none]

%-------------------------------------------------------------------------------
%	POSTER PRESENTATIONS SECTION
%-------------------------------------------------------------------------------

\section{Poster Presentations}
  \printbibliography[keyword={posterpresentations},heading=none]
  \vspace{-0.5\baselineskip}
  \begin{itemize}
    \item Awarded Sigma Xi Best Undergraduate Engineering Poster for ``A Thermal
      Test Location in a Sodium Cooled Fast Reactor''.
  \end{itemize}

%-------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%-------------------------------------------------------------------------------
 
\section{Professional Experience}

\cventry{May 2019 - August 2019}{NEUP Intern}
  {Idaho National Laboratory}{Idaho Falls, ID}{}{
  \begin{itemize}
    \item Added fast neutron cross section library capabilities to Rattlesnake neutron transport code.
    \item Used Rattlesnake to investigate effects of higher-order neutron scattering in fast reactor systems.
    \item Implemented isotopic fission spectrum mixture into Rattlesnake.
    \item Authored two technical reports related to work: 
      ``Comparison of Higher-Order Neutron Scattering Cross Sections'' (INL/EXT-19-54899) and
      ``An Analytic Benchmark for the Solution to the Isotopic Fission Spectrum Mixture Problem'' (INL/EXT-19-54998).
  \end{itemize}}

\cventry{May 2018 - August 2019}{CASL Graduate Assistant}
  {Consortium for Advanced Simulation of LWRs (CASL)}{Raleigh, NC}{}{
  \begin{itemize}
    \item Developed lesson and lectured on CTF--MPACT coupling and use for practical reactor designs.
    \item Provided technical experience and IT support for student reactor design simulations.
    \item Contributed to logistical planning for CASL Institute.
  \end{itemize}}

\cventry{May 2017 - August 2017}{NESLS Engineering Intern}
{Oak Ridge National Laboratory}{Oak Ridge, TN}{}{
  \begin{itemize}
    \item Added fast neutron cross section library capabilities to MPACT neutron transport code via ISOTXS file reader.
    \item Simulated fast neutron chloride molten salt reactor in steady-state and depletion simulations.
    \item Developed molten salt reactor models in MPACT, MCNP, and SERPENT.
    \item Proficient in large project coding and source control with 
      \texttt{git}.
  \end{itemize}}

\cventry{August 2015 - May 2017}{CASL Undergraduate Research Scholar}
{Consortium for Advanced Simulation of LWRs (CASL)}{Raleigh, NC}{}{
  \begin{itemize}
    \item Reduced computing time by 30\% by improving steam tables in COBRA-TF.
    \item Performed code comparisons to verify simulation results in MCNP and 
      MPACT.
  \end{itemize}}

\cventry{May 2016 - August 2016 \\ \vspace{5\topsep} May 2015 - August 2015}
{Edison Engineering Intern}{GE Power}{Wilmington, NC}{}{
  \begin{itemize}
    \item PRISM 
    \begin{itemize}
      \item Drafted and submitted journal article ``PRISM Reference Fuel Design.''
      \item Disclosed two patents relating to ESBWR and one patent related to PRISM.
      \item Developed PRISM General Description Book and prepared public-facing documents describing PRISM for a general audience.
    \end{itemize}
    \item LOCA \& Containment 
    \begin{itemize}
      \item Analyzed reactor transients using TRACG to support 10\% power uprate.
      \item Created automated data visualization and animation packages using MATLAB.
    \end{itemize}
  \end{itemize}}

\cventry{August 2014 - May 2017}{Licensed Reactor Operator}
{NC State PULSTAR Research Nuclear Reactor}{Raleigh, NC}{}{
  \begin{itemize}
    \item Licensed by NRC to operate all controls at NCSU reactor facility.
    \item Experienced in startup, operation, and troubleshooting on 1 MW
      research reactor.
  \end{itemize}}

%-------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%-------------------------------------------------------------------------------

\clearpage
\section{Technical Skills}

\cvcomputer{Programming Languages}{Fortran, MATLAB, Python,\\
  C++, C, \LaTeX.}
{Simulation Packages:}{DIF3D, MC\textsuperscript{2}-3, REBUS, MCNP, \\
  MPACT, CTF}
\cvcomputer{General Proficiencies}{Bash scripting, Github \& GitLab Project
  Management}{}{}

%-------------------------------------------------------------------------------
%	PROFESSIONAL DEVELOPMENT AND ACHIEVEMENTS SECTION
%-------------------------------------------------------------------------------

\section{Professional Development and Achievements}

  \cvlin {2021}{Alan F. Henry/Paul A. Greebler -- American Nuclear Scholarship.}

  \cvline{2019}{College of Engineering Master's Scholar of the Year.}

  \cvline{2017-2020}{Nuclear Engineering University Program (NEUP) Fellowship.}
  \cvlistitem{Full funding for three years of graduate school.}
  \cvlistitem{Nationally recognized Department of Energy (DOE) fellowship.}

  \cvline{2014-2017}{Nuclear Engineering University Program (NEUP) Undergraduate
    Scholarship.}

  \cvline{2017}{College of Engineering Outstanding Senior Award for Scholarly 
    Achievement \mbox{Nominee}.}
  
  \cvline{2017}{Awarded Sigma Xi Best Undergraduate Engineering Poster for ``A
    Thermal Test Location in a Sodium Cooled Fast Reactor''.}

  \cvline{2014-2018}{American Nuclear Society Scholarship.}

  \cvline{2012}{Eagle Scout.}

%%%% %-------------------------------------------------------------------------------
%%%% %	COMMUNITY INVOLVEMENT
%%%% %-------------------------------------------------------------------------------
%%%% 
%%%% \section{Community Involvement}
%%%% 
%%%%   \cvline{2017}{Mission Trip -- El Paso, TX \& Juarez, Mexico.}
%%%%   \cvlistitem{Participated in border immersion experience through \textit{Iglesia Luterana Cristo Rey} in El Paso, TX.}
%%%%   \cvlistitem{Tutored children in after school English as a Second Language program.}
%%%%   \cvlistitem{Supported new library opening in Juarez, Mexico.}
%%%% 
%%%%   \cvline{2016}{Mission Trip -- Nicaragua.}
%%%%   \cvlistitem{Volunteered at \textit{Los Papitos}, a school for special needs and disabled students.}
%%%%   \cvlistitem{Provided labor for a passion fruit farm.}
%%%% 
%%%%   \cvline{2015-2017}{Mission Trip -- Chicago.}
%%%%   \cvlistitem{Cleaned and organized a temporary home for homeless veterans.}
%%%%   \cvlistitem{Cleaned and maintained church buildings in the city.}

\end{document}
